\chapter{Rights}
\section{Figures}
\subsection{Public Domain}
Figure~\ref{fig:ucross} is released into the public domain and can therefore be used for any purpose.
Figure~\ref{fig:vhtr} is in the public domain.
Figure~\ref{fig:pbr} is in the public domain.
Figure~\ref{fig:sfr} is in the public domain.
Figure~\ref{fig:gfr} is in the public domain.
Figure~\ref{fig:swr} is in the public domain.
\subsection{World Nuclear Association}
Rights are granted for educational use for figures~\ref{fig:pwr},~\ref{fig:bwr} and~\ref{fig:phwr}
as per \url{https://www.world-nuclear.org/furniture/masterpage-items/permission-for-use-of-content.aspx}
\subsection{Canadian Nuclear Association}
Rights are granted for educational use for figure~\ref{fig:fuelelement} as per
\subsection{Terrestrial Energy Inc}
\ref{fig:MSR} is licensed under the terms of the creative commons share alike attribution required
license. \url{https://creativecommons.org/licenses/by-sa/4.0/legalcode}
\url{https://cna.ca/terms-of-use/}
\subsection{Benjamin Able}
\ref{fig:phase} was created by Benjamin Able and is licensed under the GNU free documentation license
\url{https://www.gnu.org/licenses/fdl-1.3.txt} and may therefore be used for the purpose of this
work.
\section{Equations}
\subsection{Own Creation}
Equations~\ref{decay},~\ref{fiss},~\ref{fiss2},~\ref{multfact} and~\ref{neut} were typeset by the author with
information taken from~\footcite{ReactorDesign}.

\chapter{Six Factor Formula}\label{app:sixfact}
\begin{equation}\label{sixfacteq}
    k = \eta f p \varepsilon P_{FNL} P_{TNL} = k_{\infty} P_{FNL} P_{TNL}
\end{equation}
Equation~\ref{sixfacteq} is used to calculate the multiplication factor k where\footcite{nucfundamentals}: \\
\begin{equation}
    \begin{split}
    \textit{Thermal Fission Factor}: & \eta = \frac{\nu \sigma_f^F}{\sigma_a^F} \\
    \textit{Thermal Utilisation Factor}: & f = \frac{\Sigma_a^F}{\Sigma_a} \\
    \textit{Resonance Escape Probability}: & p \approx \mathrm{exp} \left( -\frac{\sum\limits_{i=1}^{N} N_i I_{r,A,i}}{\left( \overline{\xi} \Sigma_p \right)_{mod}} \right) \\
    \textit{Fast Fission Factor}: & \varepsilon \approx 1 + \frac{1-p}{p}\frac{u_f \nu_f P_{FAF}}{f \nu_t P_{TAF} P_{TNL}} \\
    \textit{Fast Non-Leakage Probability}: & P_{FNL} \approx \mathrm{exp} \left( -{B_g}^2 \tau_{th} \right) \\
    \textit{Thermal Non-Leakage Probability}: & P_{TNL} \approx \frac{1}{1+{L_{th}}^2 {B_g}^2}
    \end{split}
\end{equation}